Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-21 paper/paper.tex
Minor changes to main and SI
Change abstract 20181021

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\newcommand{\Fig}{Fig.}
\newcommand{\hide}[1]{}
% \usepackage{lineno}
% \linenumbers

@@

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  Atomically thin graphene nanopores is emerging as one of the most
  promising candidates for next-generation membrane technology owing
  to the ultrahigh permeability. However, the size-exclusive mechanism
  limits its scalability as it remains technically challenging to
  drill subnanometer pores over a large area. Here we report
  macroscopic salt rejection through  porous graphene with
  the pore sizes of 20$\pm$10 nanometers, overcoming the pore size
  limitation set by the hydrated radii. By electrostatically gating a
  sheet of porous graphene, we report a considerable reduction of salt
  flux by up to 55\% with the gate voltage. We systematically
  investigate the effects of salt concentration and species, including
  developing a theory to model the electrolyte diffusion through a
  nanopore in a sheet of gated  graphene. The interplay
  between graphene quantum capacitance and electrical double layer is
  identified to be the main mechanism responsible for the observed
  salt rejection, when the pore size is comparable to the Debye
  screening length. Our findings reveal a new degree of freedom
  controlling the membrane potential and electrolyte permeation
  through porous two-dimensional materials.
\end{abstract}

>>>>

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\newcommand{\Fig}{Fig.}
% \usepackage{lineno}
% \linenumbers

@@

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize
  Atomically thin graphene nanopores is emerging as one of the most
  promising candidates for next-generation membrane technology owing
  to the ultrahigh permeability. However, the size-exclusive mechanism
  of selectivity limits its scalability as it remains technically
  challenging to drill subnanometer pores over a large area. Here we
  report macroscopic salt rejection through atomically-thin porous
  graphene with the pore sizes of 20$\pm$10 nanometers, overcoming the
  pore size limitation set by the hydrated radii. By electrostatically
  gating a sheet of porous graphene, we report a considerable
  reduction of salt flux by up to 55\% and 85\% with the gate voltage,
  based on our experiments and theoretical predictions,
  respectively. We systematically investigate the effects of salt
  concentration and species, including developing a theory to model
  the electrolyte diffusion through a nanopore in a sheet of gated
  graphene. The interplay between graphene quantum capacitance and
  electrical double layer is identified to be the main mechanism
  responsible for the observed salt rejection, when the pore size is
  comparable to the Debye screening length. Our findings reveal a new
  degree of freedom controlling the membrane potential and electrolyte
  permeation through porous two-dimensional materials.
  }
\end{abstract}
